supplmental

### 2019-12-31 paper_stats.Rmd
knit html
update analysis

---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: style.1.docx
  html_document:
    df_print: paged
    keep_md: true
---

@@

  library(sjPlot)
  library(tidyverse)
  library(broom)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% knitr::kable()

@@

  knitr::kable(table_df)

@@

    data <- select(df, subj_id, tx, ep) %>% 
            mutate(ep = log(ep)) %>%
            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
            filter(!is.na(ep)) %>%
            spread(tx, ep) %>% 
            mutate(effect = Active - Control) %>% 
            filter(!is.na(effect)) 
    }

@@

    data <- select(df, subj_id, tx, ep) %>% 
            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
            filter(!is.na(ep)) %>%
            spread(tx, ep) %>% 
            mutate(effect = Active - Control) %>% 
            filter(!is.na(effect)) 
    }

@@

    data <- data_frame(var = var_lab, 
                       vr = signif(sdx^2/sdy^2, 2), 
                       p = round(p, 3))

@@

  vrs_df <- do.call(bind_rows, map2(data_list, varnames,  var_ratio))

  vrs_df

@@

  # dist(sbp, "SBP (mmHg)") +
  #   ggtitle("Systolic Blood Pressure")
  # 
  # dist(dbp, "DBP (mmHg)", logged = "no") +
  #   ggtitle("Diastolic Blood Pressure")
  # 
  # dist(oxldl, "Log(OXLDL)", logged = "yes") +
  #   ggtitle("OXDL")
  # 
  # dist(art_stif, "Arterial Stiffness", logged = "no")+
  #   ggtitle("Arterial Stiffness")
  # 
  # dist(glu, "Glucose", logged = "no") +
  #   ggtitle("Glucose")
  # 
  # dist(ldl, "LDL", logged = "no") +
  #   ggtitle("LDL")
  # 
  # dist(hdl, "Log(HDL)", logged = "yes") +
  #   ggtitle("HDL")
  # 
  # dist(tchol, "Log(TCHOL)", logged = "yes")+
  #   ggtitle("Total cholesterol")
  # 
  # dist(tag, "Log(TAG)", logged = "yes")+
  #   ggtitle("TAG")
  # 
  # dist(pwa_augment, "PWA Augment", logged = "no")+
  #   ggtitle("Diastolic Blood Pressure")
  #

>>>>

---
title: ''
author: ''
date: ''
output:
  html_document:
    df_print: paged
    keep_md: true
  word_document:
    reference_docx: style.1.docx
---

@@

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(pander)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% 
  pander()

@@

  pander(table_df)

@@

    data <- select(df, subj_id, tx, ep) %>% 
      mutate(ep = log(ep)) %>%
      filter(!is.na(ep)) %>%
      spread(tx, ep) %>% 
      mutate(effect = Active - Control) %>% 
      filter(!is.na(effect)) 
    }

@@

    data <- select(df, subj_id, tx, ep) %>% 
      filter(!is.na(ep)) %>%
      spread(tx, ep) %>% 
      mutate(effect = Active - Control) %>% 
      filter(!is.na(effect)) 
    }

@@

    data <- data_frame(
      var = var_lab, 
      vr = signif(sdx^2/sdy^2, 2), 
      p = round(p, 3)
      )

@@

  df <- data.frame(
    df = I(list(sbp, dbp, c_sbp, c_dbp, art_stif, glu, hdl, ldl, oxldl,
                pwa_augment, tag, tchol)),
    var_lab = c("SBP", "DBP", "Central SBP", "Central DBP", 
                "Arterial Stiffness", "Glucose", "log(HDL)", "LDL", "log(OxLDL)", 
                "PWA Augment", "log(TAG)", "log(Total Cholesterol)"), 
    logged = c(rep("No", 6), "Yes", "No", "Yes", "No", "Yes", "Yes"),
    stringsAsFactors = FALSE
    )

  vrs_df <- do.call(bind_rows, pmap(df, var_ratio))

  pander(vrs_df)

@@

  dist(sbp, "SBP (mmHg)", logged = "no")

  dist(dbp, "DBP (mmHg)", logged = "no")

  dist(art_stif, "Arterial Stiffness", logged = "no")

  dist(glu, "Glucose", logged = "no")

  dist(hdl, "HDL", logged = "no")
  dist(hdl, "Log(HDL)", logged = "yes")

  dist(ldl, "LDL", logged = "no")

  dist(oxldl, "OXLDL", logged = "no")
  dist(oxldl, "Log(OXLDL)", logged = "yes")

  dist(pwa_augment, "PWA Augment", logged = "no")

  dist(tag, "TAG", logged = "no")
  dist(tag, "Log(TAG)", logged = "yes")

  dist(tchol, "TCHOL", logged = "no")
  dist(tchol, "Log(TCHOL)", logged = "yes")
